SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-27 quiz.tex
Remove duplicate bib entry. Shorten to 5 pages.

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is responsible for Medical Admission?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The Specification Team is responsible for}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the entity that fits the given textbook definition.\\
Stem					&\emph{What is defined by this? \enquote{X assures a defined quality of all processes and outcomes of the hospital}}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Definitions}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{What defines the term Data Warehouse System?}\\
Key						&\emph{Application component that contains data which have been extracted from other application components, in order to support either hospital management or clinical research.}\\
Distractors				&\emph{Defines the hospital’s long-term strategic goals}\\
						&\emph{An application component where the controlling rules for data processing are implemented as executable software.}\\
						&\emph{Summarizes monitored key performance indicators (KPIs) and compares them to the expected future state}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors instead form different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{Occurence}		&Asks where a term is set to exist in the used ontologies of SNIK. These ontologies are made up of relations based on the books \cite{ob} and \cite{bb}.\\
						&Stem:  In which contexts does the term \enquote{Health Insurance Company} occur? \\
Example:				&Key: Strategic Information Management \\
						&Distractor 1: Tactical Information Management \\
						&Distractor 2: Both Contexts \\
						&Distractor 3: Neither \\
\textbf{CloseMatch}		&Transfer knowledge about one textbook~\citep{bb} to the other~\citep{ob} by confirming or denying statements about entity pairs that are marked as near equivalent.\\
Stem					&\emph{In the Strategic Information Management, the Consultant is associated with the Long-Term HIS Planning, while in the Tactical Information Management, the Consultant is responsible for the Functional Specification Document.}\\
Key						&True\\
Distractor				&False\\
\bottomrule
\end{tabulary}
\end{table}

>>>>

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractor entites are wrong answers that are neighbors of degree at most 2 of the correct answer.}%, with all being of the same type, see \cref{fig:metamodel}.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is responsible for Medical Admission?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The Specification Team is responsible for}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the entity that fits the given textbook definition.\\
Stem					&\emph{What is defined by this? \enquote{X assures a defined quality of all processes and outcomes of the hospital}}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Definitions}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{What defines the term Data Warehouse System?}\\
Key						&\emph{Application component that contains data which have been extracted from other application components, in order to support either hospital management or clinical research.}\\
Distractors				&\emph{Defines the hospital’s long-term strategic goals},
						\emph{An application component where the controlling rules for data processing are implemented as executable software},
						\emph{Summarizes monitored key performance indicators (KPIs) and compares them to the expected future state}\\
\midrule
\textbf{Intertwined}	&The correct answer and distractors are connected as shown in \cref{fig:intertwined}.\\
Stem					&\emph{In the context of Strategic Information Management, which one of the following triples belongs together the most?}\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{Occurence}		&Ask whether a given term is defined in one of the textbooks \cite{bb,ob}, both or neither.\\
Stem					&\emph{In which contexts does the term \enquote{Health Insurance Company} occur?}\\
Key						&\emph{Strategic Information Management}\\
Distractors				&\emph{Tactical Information Management, Both Contexts, Neither}\\
\midrule
\textbf{CloseMatch}		&Transfer knowledge about one textbook~\citep{bb} to the other~\citep{ob} by confirming or denying statements about entity pairs that are marked as near equivalent.\\
Stem					&\emph{In the Strategic Information Management, the Consultant is associated with the Long-Term HIS Planning, while in the Tactical Information Management, the Consultant is responsible for the Functional Specification Document.} (Key: True, Distractor: False)\\
%Key						&True\\
%Distractor				&False\\
\bottomrule
\end{tabulary}
\end{table}
